Formal Analysis of Rate-Monotonic Scheduling Implementation via Real-Time Maude

### 2015-09-11 RMS/submission.tex
introduce pseudo-code

% This is LLNCS.DOC the documentation file of
% the LaTeX2e class from Springer-Verlag
% for Lecture Notes in Computer Science, version 2.4
\documentclass{llncs}
\usepackage{alltt}
\usepackage{amsmath}
%\usepackage{llncsdoc}
%
\begin{document}
%\thispagestyle{empty}
%\begin{flushleft}
%\end{flushleft}

@@

\subsection{Formulation of the Standard Setting}
The frequently used setting of the RMS algorithm for analysis
considers a task set consisting only of $n$ periodic tasks
$\tau_1,\ldots,\tau_n$. Task $\tau_i$ has a period $T_i$ and a
computation time $C_i$. First jobs of all tasks are assumed to be
instantiated simultaneously.  This means that jobs corresponding to
task $\tau_i$ are initiated at times $kT_i, k\ge 0$. The job initiated
at time $kT_i$ has $(k+1)T_i$ as its deadline, the initiation time of
the next job. The RMS algorithm chooses the labeling such that $T_1\le
T_2\le \ldots \le T_n$. Consequently, $\tau_i$ receives priority
$i$. The following assumptions are made:

@@

>>>>

% This is LLNCS.DOC the documentation file of
% the LaTeX2e class from Springer-Verlag
% for Lecture Notes in Computer Science, version 2.4
\documentclass{llncs}
\usepackage{alltt}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{algorithm}
\usepackage{algpseudocode}
%\usepackage{llncsdoc}

\newcommand{\hide}[1]{\ignorespaces}

\begin{document}
%\thispagestyle{empty}
%\begin{flushleft}
%\end{flushleft}

@@

\subsection{Formulation of the Standard Setting}
The frequently used setting of the RMS algorithm for analysis
considers a task set consisting only of $n$ periodic tasks
$\tau_1,\ldots,\tau_n$. Task $\tau_i$ has a period $T_i$ and a
computation time $C_i$. First jobs of all tasks are assumed to be
instantiated simultaneously. This means that jobs corresponding to
task $\tau_i$ are initiated at times $kT_i, k\ge 0$. Deadlines consist
of runability constraints only, that is, the job initiated at time
$kT_i$ has $(k+1)T_i$ as its deadline, which is the initiation time of
the next job. The RMS algorithm chooses the labeling such that $T_1\le
T_2\le \ldots \le T_n$. Consequently, $\tau_i$ receives priority
$i$. The following assumptions are made:

@@

In this paper, our application of the RMS algorithm meets the
assumption~(A2), while we would try to relax (A1) and (A3) in our
analysis model.

\subsection{The Implementation of RMS}
The algorithm of the RMS is straightforward, and it is easy to
implement it in pratical systems. However, the way to implement it is
not unique. Our target implementation to analyze is from a realistic
avionic operating system. Interrupts triggered by the clock would come
every $T$, which we call \emph{interrupt cycle}. When an interrupt
request comes, if the system is interruptable, i.e. the interrupt
switch is enabled, the funtion $schedule()$ will be called; otherwise
$schedule()$ will be called once the interrupt switch becomes enable.
The pseudo code of $schedule()$ is shown as
Algorithm~\ref{a:schedule}, where $taskList$ is the list of periodic
tasks, which are needed to be scheduled, and assumed ordered
descendingly by priorities, and where both variables $taskList$ and
$timer$ are global. In this implementation, the period $T_i$ of each
task is a multiple of $T$, and the tasks are independent, meeting the
assumption~(A2).

\begin{algorithm}
  \caption{The C-Like Pseudo Code of $schedule()$}
  \label{a:schedule}
  \begin{algorithmic}[1]
\Function{$schedule$}{$ $}{}
  \State \Call{$int\_o\!f\!\!f$}{$ $}; \Comment{to disable interrupts}
  \State \Call{$updateStatus$}{$taskList$};
  \State $timer = timer + 1$;
  \State $p = taskList$;
  \While{$p$} 
    \If{$p\rightarrow status == \textit{INTERRUPT}$}
      \State \Return;
    \ElsIf{$p\rightarrow status == \textit{READY}$}      
      \State $p\rightarrow status = \textit{RUNNING}$;
      \State \Call{$int\_on$}{$ $}; \Comment{to enable interrupts}
      \State $p\rightarrow function()$; \Comment{to run the task}
      \State \Call{$int\_o\!f\!\!f$}{$ $};
      \State $p\rightarrow status = \textit{DORMANT}$;
    \EndIf
    \State $p = p\rightarrow next$;
  \EndWhile
\EndFunction
\Function{$updateStatus$}{$p$}
  \While{$p$}
    \If{$p\rightarrow status == \textit{RUNNING}$}
      \State $p\rightarrow status = \textit{INTERRUPT}$;
    \EndIf
    \If{$timer~\%~(p\rightarrow period) == 0$} \Comment{the task should be initiated}
      \If{$p\rightarrow status == \textit{DORMANT}$} 
        \State $p\rightarrow status = \textit{READY}$;
      \Else \Comment{the status is \textit{READY} or \textit{INTERRUPT}}
	\State \Call{$reportTaskError$}{$p$}; \Comment{the task misses its deadline}
      \EndIf
    \EndIf
    \State $p = p\rightarrow next$;
  \EndWhile
\EndFunction
  \end{algorithmic}
\end{algorithm}
